FraCaS: Temporal Analysis

### 2020-10-28 paper2020/paper.tex
finish checking examples and update paper

\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}[hbt]
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#FraCaS
                          & This        & FC2         & FC & MINE & Nut  & LP  \\ \hline
Quantifiers  & 75         & .91        & .96         & .96    & .77  & .53  & .93  \\
             &            & \ncases{74}& \ncases{74} &        &      &      &     \ncases{44} \\
Plurals      & 33         & .64        & .82         & .76    & .67  & .52  & .73 \\
             &            &            &             &     &   &   & \ncases{24} \\
Anaphora     & 28         & .79        & .86         &   -    & -    & -    &  -       \\
Ellipsis     & 52         & .81        & .87         &   -    & -    & -    &  -       \\
Adjectives   & 22         & .95        & .95         & .95    & .68  & .32  & .73 \\
             &            & \ncases{20}&  \ncases{20}&     &   &   &  \ncases{12} \\
Comparatives & 31         & .64        & .87         & .56    & .48  & .45  &  -       \\
Temporal     & 75         & .71        &  -          &   -    &   -  &  -   &  -       \\
Verbs        & 8          & .75        & .75         &   -    & -    & -    &  -       \\
Attitudes    & 13         & .85        & .92         & .85    & .77  & .46  & .92  \\ 
             &            &            &             &        &      &      & \ncases {9}  \\ \hline
Total        & 337        & .78        & .89         & .83    & .69  & .50  & .85  \\
             &            & \ncases{329}& \ncases{259}& \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Accuracy of our system compared to others.
    ``This" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the second column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FC''
    refers to the work of \citet{bernardy_type-theoretical_2017}, and ``FC2'' its followup~\citep{bernardy_wide-coverage_2019}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} \cite{bos:2008}, and ``Langpro"
    to the system presented by \citet{abzianidze_tableau_2015}. A dash
    indicates that no attempt was made for the section. }
  \label{tab:results}
\end{table}
\paragraph{interaction with negation and group readings}
One reason explaining the lower performance of our system on some
sections of the testsuite is that our interpretation of time interacts
imperfectly with negation and group readings.

The issue is that the quantification introduced by the temporal marker
is outside the negation. For example, the premiss of (038) is
interpreted as ``there exists a time in the past when every delegate
did not finish the report'' --- which is incorrect in this context.
\fracasex{038}{
\item	No delegate finished the report.
\hyp 	Some delegate finished the report on time.
}
%
We stress that such interaction between quantifiers and negation
already occurs without any temporal analysis: one must make a difference
between narrow  and wide scope.\footnote{The literature on wide and narrow scope readings of quantifiers and quantifiers and negation is vast. We direct the reader to \cite{steedman:2012} for a comprehensive and thorough discussion of the relevant issues.} Unfortunately,
the Montagovian system over which we base our implementation does not
support these phenomena. (In fact the FraCaS test suite does not appear to
test if the difference between narrow and wide scoping is handled properly.)
We propose that the situation becomes
quantitatively more difficult to handle with the added complication of
time-quantification, but not fundamentally different.
%
A similar issue occurs with group readings, which are interpreted as
conjunctions. Here, the problem is an improper resolution of scoping
order, between this conjunction and time-interval quantifiers.

>>>>

\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}[hbt]
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#FraCaS
                          & This        & FC2         & FC & MINE & Nut  & LP  \\ \hline
Quantifiers  & 75         & .93        & .96         & .96    & .77  & .53  & .93  \\
             &            & \ncases{74}& \ncases{74} &        &      &      &     \ncases{44} \\
Plurals      & 33         & .76        & .82         & .76    & .67  & .52  & .73 \\
             &            &            &             &     &   &   & \ncases{24} \\
Anaphora     & 28         & .79        & .86         &   -    & -    & -    &  -       \\
Ellipsis     & 52         & .81        & .87         &   -    & -    & -    &  -       \\
Adjectives   & 22         & .95        & .95         & .95    & .68  & .32  & .73 \\
             &            & \ncases{20}&  \ncases{20}&     &   &   &  \ncases{12} \\
Comparatives & 31         & .65        & .87         & .56    & .48  & .45  &  -       \\
Temporal     & 75         & .71        &  -          &   -    &   -  &  -   &  -       \\
Verbs        & 8          & .75        & .75         &   -    & -    & -    &  -       \\
Attitudes    & 13         & .85        & .92         & .85    & .77  & .46  & .92  \\ 
             &            &            &             &        &      &      & \ncases {9}  \\ \hline
Total        & 337        & .80        & .89         & .83    & .69  & .50  & .85  \\
             &            & \ncases{329}& \ncases{259}& \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Accuracy of our system compared to others.
    ``This" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the second column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FC''
    refers to the work of \citet{bernardy_type-theoretical_2017}, and ``FC2'' its followup~\citep{bernardy_wide-coverage_2019}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} \cite{bos:2008}, and ``Langpro"
    to the system presented by \citet{abzianidze_tableau_2015}. A dash
    indicates that no attempt was made for the section. }
  \label{tab:results}
\end{table}
\paragraph{interaction with group readings}
One reason explaining the lower performance of our system on some
sections of the testsuite is that our interpretation of time interacts
imperfectly with group readings.

We stress that group readings is already flawed in the system which we base our analysis on.
The issue is related to the difference
between narrow  and wide scope.\footnote{The literature on wide and narrow scope readings of quantifiers and quantifiers and negation is vast. We direct the reader to \cite{steedman:2012} for a comprehensive and thorough discussion of the relevant issues.} (In fact the FraCaS test suite does not appear to
test if the difference between narrow and wide scoping is handled properly.)
We propose that the situation becomes
quantitatively more difficult to handle with the added complication of
time-quantification, but not fundamentally different.
